Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-04 volunteer-clouds-ieee-ci-si.tex
una falta
changing some words
adding some sentences
adding Trap-function citation

\author{Juan-J.~Merelo*$^1$, Mario Garcia-Valdez$^2$, Pedro A. Castillo$^1$, Pablo Garc\'a-S\'anchez$^1$
\thanks{Manuscript submitted for review on \today.}%
\thanks{$^1$Dept. of Computer Architecture and Technology and CITIC University of Granada}%
\thanks{$^2$Dept. of Graduate Studies at Instituto Tecnologico de Tijuana}%
\thanks{E-mail addresses: {\tt jmerelo@ugr.es}, {\tt
    mario@tectijuana.edu.mx}, {\tt pacv@ugr.es}, {\tt pablogarcia@ugr.es}}%
\thanks{*Corresponding author.}%
}

@@

In general, a volunteer-based distributed evolutionary computation
system based on the browser is simply a client-server architecture
whose client is, or can be, embedded in the browser via
JavaScript. All parts of the system are free and available with a free
license from \url{https://github.com/JJ/splash-volunteer}.
Thus, {\sf NodIO} has two parts:\begin{enumerate}
\item A REST server, that is, a server that includes several remote
  requests for storing and retrieving information (the CRUD cycle:
  create, request, update and delete) from the server. The information
  is of two kinds: {\em problem} based, that is, related to the
  evolutionary algorithm such as {\tt PUT}ing a chromosome in or {\tt
    GET}ing a random chromosome from it. It also peforms logging
  duties, but is basically a very lightweight and hign performance
  data store \cite{jj:idc:lowcost}. The server has the capability to
  run a single experiment, storing the chromosomes in a data structure
  that is reset when the solution is found. 
\item A client that includes the evolutionary algorithm as 
  JavaScript code embedded in a web page that displays graphs and some
  additional links and information on the experiment. This code runs
  an evolutionary algorithm {\em island} starting with random
  population and sending, every 100 generations, the best individual
  back to the server (via a {\tt PUT} request) and requesting a random
  individual from the server (via a {\tt GET} request). Apart from
  these constants, the algorithm can be run in many different ways:
  stopping when solution is found or, as we have done in this paper,
  using WebWorkers, which run in the background even if the webpage or
  browser tab with the experiment is not currently on focus.  
\end{enumerate}

Figure \ref{fig:system} describes the general system architecture.
%
\begin{figure}[!t]
\centering
\includegraphics[width=4in]{img/system.pdf}
\caption{Description of the used system. Clients execute a JS EA in the browser, which, every 100 generations, sends the best individual and receives a random one from the server. } 
\label{fig:system}
\end{figure}

The researcher only has to change a function to solve a different
problem, in this case the classical Trap function has been %FERGU: cita a Trap function
used. JavaScript is a functional language and declaring a different
function and handling at the creation of the algorithm object, called %FERGU: poner algo tras el handling: handling it?
{\tt Classic} is the only change needed to work with a different
problem. Let us see how this system addresses the different challenges
outlined in the State of the Art:\begin{itemize}
\item {\em Scalability} is provided via the use of a lightweight and
  high-performance, single-threaded, server based in NodeJS and
  Express.js. Although this single server is a bottleneck since it
  will eventually saturate, the fact that it runs as a single thread
  allows the service of many requests. In fact, a limit with the
  number of simultaneous requests will be reached, but so far it has
  not been found, unlike what we found in our previous systems, DCoR,
  \cite{gecco07:workshop:dcor}, which had a low scalability.
\item The system is {\em heterogeneous} since it does not need any
  performance, operating system or even browser requirement: anyone
  visiting the page, even from mobile devices, can load the algorithm. %Fergu: puesto lo de mobile devices para venderlo aún mejor
\item {\em Fault tolerance} is always an issue, and in this case, the
  single point of failure would be the server: the system, as such,
  would break down if the server fails. However, the individual
  islands in every browser would continue running, and having access
  to just one of them would allow the local algorithm to proceed. In
  fact, the island does not need the server to run: it runs locally if
  needed, with the only exception that it is obviously unable to
  communicate with the rest of the islands.
\item {\em Adaptiveness} is achieved simply through autonomous
  operation of every individual island and no synchronization
  mechanism. The islands in the system are, in fact, unaware of each
  other, communicating only through the server.
\item Since the algorithm is run on the browser, {\em safety} is
  achieved through its sandbox mechanisms. The user is thus assured
  that there is no unsafe access either to their local files or even
  to more resources that the browser should be allotted.
\item Running the algorithm is just a matter of loading the page,
  which means that operation is totally {\em anonymous}. For the same
  reason, {\em ease of use} is optimal, being as easy as simply
  clicking on an URL and available to anyone with access to a browser.
\item {\em Reasonable performance} is not ensured. In fact, we should
  make sure that there is a reasonable amount of clients over which
  the performance achieved is bigger than what you would obtain in
  your own desktop system. If that is not done, it is a pointless
  academic exercise.
\end{itemize}

>>>>

\author{Juan-J.~Merelo*$^1$, Mario Garcia-Valdez$^2$, Pedro A. Castillo$^1$, Pablo Garc\'ia-S\'anchez$^1$
\thanks{Manuscript submitted for review on \today.}%
\thanks{$^1$Dept. of Computer Architecture and Technology and CITIC University of Granada}%
\thanks{$^2$Dept. of Graduate Studies at Instituto Tecnologico de Tijuana}%
\thanks{E-mail addresses: {\tt jmerelo@ugr.es}, {\tt
    mario@tectijuana.edu.mx}, {\tt pacv@ugr.es}, {\tt pablogarcia@ugr.es}}%
\thanks{*Corresponding author.}%
}

@@

In general, a volunteer-based distributed evolutionary computation
system based on the browser is simply a client-server architecture
whose client is, or can be, embedded in the browser via JavaScript.

% [Pedro] desde el abstract no se había nombrado "NodIO". 
% Creo que en este párrafo debería introducirse, principalmente el nombre.
% Añado una frase presentándolo:
In this sense, in this paper we propose {\sf NodIO}, a PaaS based 
volunteer computing system, whose architecture
has been developed using JavaScript on both the client and server sides.
All parts of the system are free and available with a free
license from \url{https://github.com/JJ/splash-volunteer}.
Thus, {\sf NodIO} has two parts:\begin{enumerate}
\item A REST server, that is, a server that includes several remote
  requests for storing and retrieving information (the CRUD cycle:
  create, request, update and delete) from the server. The information
  is of two kinds: {\em problem} based, that is, related to the
  evolutionary algorithm such as {\tt PUT}ing a chromosome in or {\tt
    GET}ing a random chromosome from it. It also peforms logging
  duties, but is basically a very lightweight and hign performance
  data store \cite{jj:idc:lowcost}. The server has the capability to
  run a single experiment, storing the chromosomes in a data structure
  that is reset when the solution is found. 
\item A client that includes the evolutionary algorithm as 
  JavaScript code embedded in a web page that displays graphs and some
  additional links and information on the experiment. This code runs
  an evolutionary algorithm {\em island} starting with random
  population and sending, every 100 generations, the best individual
  back to the server (via a {\tt PUT} request) and requesting a random
  individual from the server (via a {\tt GET} request). Apart from
  these constants, the algorithm can be run in many different ways:
  stopping when solution is found or, as we have done in this paper,
  using WebWorkers, which run in the background even if the webpage or
  browser tab with the experiment is not currently on focus.  
\end{enumerate}

Figure \ref{fig:system} describes the general system architecture.
%
\begin{figure}[!t]
\centering
\includegraphics[width=4in]{img/system.pdf}
\caption{Description of the proposed system. Clients execute a JS EA in the browser, which, every 100 generations, sends the best individual and receives a random one from the server. } 
\label{fig:system}
\end{figure}

The researcher only has to change a function to solve a different
problem, in this case the classical Trap function \cite{Ackley1987} has been %FERGU: cita a Trap function
used. JavaScript is a functional language and declaring a different
function and handling at the creation of the algorithm object, called %FERGU: poner algo tras el handling: handling it?
{\tt Classic} is the only change needed to work with a different
problem. Let us see how this system addresses the different challenges
outlined in the State of the Art:\begin{itemize}
\item {\em Scalability} is provided via the use of a lightweight and
  high-performance, single-threaded, server based in NodeJS and
  Express.js. Although this single server is a bottleneck since it
  will eventually saturate, the fact that it runs as a single thread
  allows the service of many requests. In fact, a limit with the
  number of simultaneous requests will be reached, but so far it has
  not been found, unlike what we found in our previous systems, DCoR,
  \cite{gecco07:workshop:dcor}, which had a low scalability.
\item The system is {\em heterogeneous} since it does not need any
  performance, operating system or even browser requirement: anyone
  visiting the page, even from mobile devices, can load the algorithm. %Fergu: puesto lo de mobile devices para venderlo aún mejor
\item {\em Fault tolerance} is always an issue, and in this case, the
  single point of failure would be the server: the system, as such,
  would break down if the server fails. However, the individual
  islands in every browser would continue running, and having access
  to just one of them would allow the local algorithm to proceed. In
  fact, the island does not need the server to run: it runs locally if
  needed, with the only exception that it is obviously unable to
  communicate with the rest of the islands.
\item {\em Adaptiveness} is achieved simply through autonomous
  operation of every individual island and no synchronization
  mechanism. The islands in the system are, in fact, unaware of each
  other, communicating only through the server.
\item Since the algorithm is run on the browser, {\em safety} is
  achieved through its sandbox mechanisms. The user is thus assured
  that there is no unsafe access either to their local files or even
  to more resources that the browser should be allotted.
\item Running the algorithm is just a matter of loading the page,
  which means that operation is totally {\em anonymous}. For the same
  reason, {\em ease of use} is optimal, being as easy as simply
  clicking on an URL and available to anyone with access to a browser.
\item {\em Reasonable performance} is not ensured. In fact, we should
  make sure that there is a reasonable amount of clients over which
  the performance achieved is bigger than what you would obtain in
  your own desktop system. If that is not done, it is a pointless
  academic exercise.
\end{itemize}
